stupid backoff

### 2019-11-19 al_stup.Rmd
data.table modifications

1. create frequency tables and n-grams
```{r}
getFreqs = function(dat, ng) {
        dat.dfm = dfm(dat, ngrams = ng, remove_punct = T, remove_numbers = T
                      #,remove = stopwords("english")
                      )
        dat.freq = docfreq(dat.dfm)
        dat.freq = dat.freq[sort(names(dat.freq))] 
        return(dat.freq)
}

getTables = function(dat, ng) {
        ngrams = getFreqs(dat = dat, ng = ng)
        ngrams_dt = data.table(ngram = names(ngrams), freq = ngrams)
        return(ngrams_dt)
}

>>>>

1. create frequency tables and n-grams
```{r}
getTables = function(dat, ng) {
    dat.dfm = dfm(dat, ngrams = ng, remove_punct = T, remove_numbers = T)
    dat.tbl = data.table(ngram = featnames(dat.dfm), count = colSums(dat.dfm),
                         key = "ngram")
    dat.tbl = dat.tbl[order(ngram)]
    return(dat.tbl)
}
